# brandwatchR

An API wrapper package for the [Brandwatch API](https://developers.brandwatch.com/docs/).

If you're like me and you just want to get your hands on lots of lovely mention data, you do that by:

- Authenticating with `bwr_auth()`
- Working out the project id you need with `bwr_get_projects()`
- Working out the id of the query you want results for with `bwr_get_queries()`.

From here, you can retrieve mentions data using `bwr_get_mentions()`, which takes the project ID and query ID as arguments.


## Install

```{r}
devtools::install_github("Phippsy/brandwatchR")
```

## Authenticate

Only username and password are mandatory. 
You can optionally specify `refresh = TRUE` to force the function to obtain a new token from the API. Otherwise it will read a cached local file if available. 
You can also optionally specify `cache = FALSE` if you prefer not to have your token cached locally. In this case, your token will be stored in a local environment variable and available for the current R session only.

```{r}
bwr_auth(username = "your@username.com",
         password = "your_password",
         refresh = TRUE,
         cache = TRUE)
```

## Get project info

```{r}
my_projects <- bwr_get_projects()
head(my_projects)
```

This will display a data frame of project information including project ID, description, creation date and more.

Read the [Brandwatch documentation for more info](https://developers.brandwatch.com/docs/retrieving-projects)


## Get queries for a project

Once you have a project ID, you can find out all the available queries in your environment. Do this using the `bwr_get_queries()` function:

```{r}
# We arbitrarily pull the first available project ID
my_project <- bwr_get_projects()$id[1]

# Get list of queries for this project ID
my_query <- bwr_get_queries(project_id = my_project)
```

This will return a data frame showing you the ID, name, created date and similar metadata for the queries in the specified project.

## Get mentions for a query

Finally, the fun stuff - we can now request all mentions for a given query, using a specified date range. We achieve that using the `bwr_get_mentions()` function.

```{r}
my_mentions <- bwr_get_mentions(
  project_id = my_project,
  query_id = my_query,
  date_range = c("2018-01-01", "2018-02-01"))
```

This will return a data frame containing the mentions for your specified query. Brandwatch returns a *ton* of fields in the API response, so it's likely that you'll want to slim down the resulting data frame by using `dplyr`'s `select()` function or similar.

You can find information about the mention field definitions within [Brandwatch's API documentation](https://developers.brandwatch.com/docs/mention-metadata-field-definitions).
