# brandwatchR

An API wrapper package for the [Brandwatch API](https://developers.brandwatch.com/docs/).

Work in progress...


## Install

```{r}
devtools::install_github("Phippsy/brandwatchR")
```

## Authenticate

Only username and password are mandatory. 
You can optionally specify `refresh = TRUE` to force the function to obtain a new token from the API. Otherwise it will read a cached local file if available. 
You can also optionally specify `cache = FALSE` if you prefer not to have your token cached locally. In this case, your token will be stored in a local environment variable and available for the current R session only.

```{r}
bwr_auth(username = "your@username.com",
         password = "your_password",
         refresh = TRUE,
         cache = TRUE)
```

## Get project info

```{r}
my_projects <- bwr_get_projects()
head(my_projects)
```

This will display a data frame of project information including project ID, description, creation date and more.
[Brandwatch documentation for more info](https://developers.brandwatch.com/docs/retrieving-projects)
